Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-01-19 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
minor changes

# table
table_result_combined <- kbl(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(Z)$ for different values of $L$, and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "c",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined"
) %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
   kable_styling(latex_options = "scale_down")
 # kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

@@

## Real SAR Images

@@

 colnames(resultados_df) <- c("Area", "mean", "$\\widehat{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{C}}$", "$H_{\\Gamma_{\\text{SAR}}}$", "$S(Z)$")

>>>>

# table
table_result_combined <- kbl(
  combined_summary_stats,
  caption = "Descriptive analysis of $S(\\bm Z; L)$ for different values of $L$, and $\\mu=1$.",
  format = "latex",
  booktabs = TRUE,
  align = "c",
  escape = FALSE,
  digits = 4,
  label = "table_stat_combined"
) %>%
  collapse_rows(latex_hline = "major", valign = "middle") %>%
   kable_styling(latex_options = "scale_down")
 # kable_styling(latex_options = c("striped", "hold_position"), full_width = FALSE)

@@

## SAR Images

@@

 colnames(resultados_df) <- c("Area", "mean", "$\\widehat{H}_{\\text{C}}$", "$\\widetilde{H}_{\\text{C}}$", "$H_{\\Gamma_{\\text{SAR}}}$", "$S(\\bm Z)$")
